---
output: github_document
---
## Packages

```{r, RefineGeo_package, warning = FALSE, message = FALSE}
# install.packages("devtools")
devtools::install_github("PedroTL/RefineGeo")
library(tidygeocoder)
library(knitr)
library(dplyr)
```

## Geocoding Data Preparation

To start, we can acquire a sample data frame from the `RefineGeo` package. Typically, address information is distributed across separate columns. Here, we will assemble a complete address, which will serve as the input for Geocoding across three distinct services.

```{r, warning = FALSE, message = FALSE}
sample_address <- RefineGeo::sample_address

knitr::kable(head(sample_address), align = "c")
```

The address information usually can be giving in separate columns. Here we are going to make a complete address, being the input for Geocoding in three different services.

```{r, warning = FALSE, message = FALSE}
# Creating a full address as input
sample_address <- sample_address %>%
  mutate(input_addr = RefineGeo::clean_address(paste(address,
                                                     municipality,
                                                     state,
                                                     cep,
                                                     country,
                                                     sep = " ")))

knitr::kable(head(sample_address), align = "c")
```

### Geocoding Combination

Next, we'll utilize `tidygeocoder::geocode_combine` to extract Latitude, Longitude, and output addresses from three different Geocoding services: Arcgis, Bing, and Here.

```{r, warning = FALSE, message = FALSE}
response <- 
  tidygeocoder::geocode_combine(
  sample_address,
  queries = list(
    list(method = 'arcgis', mode = 'single'),
    list(method = 'bing', mode = 'single'),
    list(method = 'here', mode = 'single')
  ),
  global_params = list(address = 'input_addr', full_results = TRUE),
  cascade = FALSE,
  return_list = TRUE
)
```

For Bing and Here services, it's necessary to set an API key in the environment. You can use `usethis::edit_r_environ()` to set `BINGMAPS_API_KEY = "Your_API_KEY"` and `HERE_API_KEY = "Your_API_KEY"`. When dealing with multiple addresses, consider using the `mode = 'batch'` argument and refer to `tidygeocoder::batch_limit_reference`. Approximately 3 minutes are required to obtain full results for all Geocoding services when dealing with 100 addresses.

### Retrieving Responses for Each Service

From the responses, our primary interest lies in obtaining the Latitude, Longitude, and the corresponding returned address.

```{r, warning = FALSE, message = FALSE}
arcgis_response <- response$arcgis
arcgis_response <- arcgis_response %>%
  select("input_addr", "input_cep" = "cep", "output_addr_1" = "arcgis_address", "lon1" = "location.x", "lat1" = "location.y") %>%
  as.data.frame()

knitr::kable(head(arcgis_response), align = "c")
```

This process is then repeated for the other two services.

```{r, warning = FALSE, message = FALSE}
bing_response <- response$bing
bing_response <- bing_response %>%
  select("input_addr", "input_cep" = "cep", "output_addr_2" = "name", "lon2" = "long", "lat2" = "lat") %>%
  as.data.frame()

knitr::kable(head(bing_response), align = "c")
```

```{r, warning = FALSE, message = FALSE}
here_response <- response$here
here_response <- here_response %>%
  select("input_addr", "input_cep" = "cep", "output_addr_3" = "here_address.label", "output_addr_cep_3" = "here_address.postalCode" ,"lon3" = "long", "lat3" = "lat") %>%
  as.data.frame()

knitr::kable(head(here_response), align = "c")
```

### Compiling a Final Dataset

```{r, warning = FALSE, message = FALSE}
sample_address_geo <-
  plyr::join_all(list(arcgis_response,
                      bing_response,
                      here_response),
                 by = c("input_addr", "input_cep"),
                 type = 'left') %>%
  mutate("output_addr_cep_1" = RefineGeo::extr_cep(output_addr_1),
         "output_addr_cep_2" = RefineGeo::extr_cep(output_addr_2),
         "output_addr_cep_3" = RefineGeo::extr_cep(output_addr_cep_3),
         "input_cep" = as.character(input_cep),
         "output_addr_1" = RefineGeo::clean_address(output_addr_1),
         "output_addr_2" = RefineGeo::clean_address(output_addr_2),
         "output_addr_3" = RefineGeo::clean_address(output_addr_3)) %>%
  select("input_addr", "input_cep", "output_addr_1", "output_addr_2", "output_addr_3", "output_addr_cep_1", "output_addr_cep_2", "output_addr_cep_3", "lat1", "lon1", "lat2", "lon2", "lat3", "lon3")

knitr::kable(head(sample_address_geo), align = "c")
```

It's noteworthy that the `Here` Geocoding service provides the `PostCode` column already, requiring minimal cleaning. Depending on the chosen service, it's advisable to review all outputs before selecting variables. In essence, the optimal data set structure is outlined. Now, `RefineGeo` can be utilized to gain a more accurate perspective on the quality of the provided coordinates.

This data is available in `RefineGeo::sample_address_geo`








